---
title: "homework_4_Tan_Xinmiao"
author: "Xinmiao Tan"
date: "July 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: [https://github.com/xinmiaotan/compscix-415-2-assignments](https://github.com/xinmiaotan/compscix-415-2-assignments)

```{r load_packages, warning=FALSE, message=FALSE}
library(nycflights13)
library(tidyverse)
```

## Section 5.6.7: #2, #4 and #6 only. Extra Credit: Do #5 Section 10.5: #1, #2, #3 and #6 only

### 2. Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).
```{r}
not_cancelled <- flights %>% filter(!is.na(dep_delay),!is.na(arr_delay))
not_cancelled %>% count(dest) 
not_cancelled %>% count(tailnum, wt = distance) 

not_cancelled %>% group_by(dest) %>% summarise(n=n())
not_cancelled %>% group_by(tailnum) %>% summarise(n=sum(distance))
```

### 4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?
```{r}
flights %>% 
    group_by(year,month,day) %>% 
    summarise(cancelled_perc=mean(is.na(dep_delay)),
              mean_dep=mean(dep_delay,na.rm=T),
              mean_arr=mean(arr_delay,na.rm=T)) %>%
    ggplot(aes(y=cancelled_perc))+
    geom_point(aes(x=mean_dep),colour='red')+
    geom_point(aes(x=mean_arr),colour='blue')+
    labs(x='avg delay per day',y='cancelled flights perc')
```

The highter the average delay of the day, the higher the percentage of cancelled filgths per day.

### 6. What does the sort argument to count() do. When might you use it?

When you want to sort according to count.

```{r}
flights %>% count(flight,sort=T)
```

### 1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

```{r}
print(mtcars)
class(mtcars)
class(as_tibble(mtcars))
```

Tibbles only print out a limited number of rows and shows the calss on top of each column.
Tibbles have class: tbl_df, tbl_ and data.frame.


### 2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]

tbl <- as_tibble(df)
tbl$x
tbl[, "xyz"]
tbl[, c("abc", "xyz")]
```

Data frame can extract columns with partially match when using $. But tibble can only extract data with completely match when using $.

### 3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

```{r}
df <- data.frame(abc = 1, xyz = "a",mpg = 50)
var <- "mpg"
df$var
df[[var]]
```

We can use [[]] to extract that column.

### 6. What option controls how many additional column names are printed at the footer of a tibble?

```{r}
?print.tbl_df
```

n_extra.
Number of extra columns to print abbreviated information for, if the width is too small for the entire tibble. If NULL, the default, will print information about at most tibble.max_extra_cols extra columns.

## Section 12.3.3: #2, #3 and #4 only

### 2. Why does this code fail?

```{r}
table4a %>% 
  gather('1999', '2000', key = "year", value = "cases")
```

1999 and 2000 need to be ''.


### 3. Why does spreading this tibble fail? How could you add a new column to fix the problem?

```{r}
people <- tribble(
  ~name,             ~key,    ~value, ~obs,
  #-----------------|--------|------|------
  "Phillip Woods",   "age",       45, 1,
  "Phillip Woods",   "height",   186, 1,
  "Phillip Woods",   "age",       50, 2,
  "Jessica Cordero", "age",       37, 1,
  "Jessica Cordero", "height",   156, 1
)
glimpse(people)
spread(people,key,value)
```

Because row 1 and row 3 have the same name and key.


### 4. Tidy the simple tibble below. Do you need to spread or gather it? What are the variables?

```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
print(preg)

gather(preg,sex,count,male,female) %>%
    mutate(pregnant = pregnant == 'yes',
           female = sex =='female') %>%
    select(-sex)
```

Need to be gathered. 
Pregnant: false or true, female: false or true, count: integer.

## Section 12.4.3: #1 and #2 only

### 1. What do the extra and fill arguments do in separate()? Experiment with the various options for the following two toy datasets.

```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra='drop')

tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra='merge')

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill ='right')

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill='left')
```

The extra arguments tells what to do when too many pieces. drop: drop the extra pieces. merge: merge the extra pieces into one.
The fill argument tells what to do when pieces is less. Right: fill the right pieces with NA. Left: fill the left pieces with NA. 

### 2. Both unite() and separate() have a remove argument. What does it do? Why would you set it to FALSE?

```{r}
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill='right')

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill='right', remove=FALSE)
```

Set the remove argument to False will keep the old one.

## Answer these questions:
## Follow these steps:
- Download the baby_names.txt file from Canvas which is in the Homework 4 assignment section.

- Load this file into R correctly and take a glimpse of the output.
- Export this file as a csv file and call it ‘baby_names.csv’.
- Reload the baby_names.csv file and take another glimpse.
- Show all of your code and the output. There should be two data import lines of code, one data export line of code, and two glimpses of the data.

```{r}
file_path <- '/Users/xinmiaotan/Desktop/Data Science/R/IntroR/Lec4/baby_names.txt'
bany_names_txt <- read_delim(file = file_path,delim = '|')
glimpse(bany_names_txt)
write_csv(bany_names_txt, path = '/Users/xinmiaotan/Desktop/Data Science/R/IntroR/Lec4/baby_names.csv')
file_path <- '/Users/xinmiaotan/Desktop/Data Science/R/IntroR/Lec4/baby_names.csv'
bany_names_csv <- read_csv(file = file_path)
glimpse(bany_names_csv)
```
